Point estimates comparison for the simplified Naomi model

### 2023-07-20 src/docs_paper/appendix.Rmd
Add tables of point estimate estimation results to appendix #55

## Estimated normalising constant comparison

@@

# Comprehensive inference comparison

In this section we give further inference comparison results, parameter by parameter.

@@

@@

@@

ks_summary %>%
  ungroup() %>%
  filter(type == "Latent field") %>%
  select(-type) %>%
  rename(TMB = `KS(TMB, tmbstan)`, `PCA-AGHQ` = `KS(aghq, tmbstan)`) %>%
  select(Parameter, TMB, `PCA-AGHQ`) %>%
  mutate(Difference = TMB - `PCA-AGHQ`) %>%
  gt::gt() %>%
  gt::summary_rows(
   columns = c(`TMB`, `PCA-AGHQ`, Difference),
   fns = list(Average = ~ mean(.x)),
   formatter = gt::fmt_number,
   decimals = 3
  ) %>%
  gt::fmt_number(
    columns = c(`TMB`, `PCA-AGHQ`, Difference),
    decimals = 3
  ) %>%
  gt::text_transform(
    locations = gt::cells_body("Parameter"),
    fn = function(x) paste0("\\texttt{", x, "}")
  ) %>%
  gt::text_transform(
    locations = gt::cells_body("Difference"),
    fn = function(x) ifelse(x > 0, paste0("\\textbf{", x, "}"), paste0(x))
  ) %>%
  gt::as_latex() %>%
  as.character() %>%
  cat(file = "ks-summary.tex")
```

>>>>

## Normalising constant estimation

@@

# Inference comparison

In this section we give more detailed inference comparison results for each parameter or group of parameters.
For any parameter with length greater than one, the results presented are an average.

@@

### Posterior mean

```{r}
point_summary <- read_csv("depends/point-estimates.csv")

point_summary <- point_summary %>%
  mutate(type = fct_recode(type, "Output" = "output", "Latent" = "latent"))

latex_table_point_estimates <- function(.indicator) {
  point_summary %>%
  group_by(par, type, indicator, method) %>%
  summarise(
    rmse = sqrt(mean((truth - approximate)^2)),
    mae = mean(abs(truth - approximate))
  ) %>%
  ungroup() %>%
  pivot_wider(
    names_from = "method",
    values_from = c("rmse", "mae")
  ) %>%
  filter(indicator == .indicator) %>%
  select(Parameter = par, Type = type, `TMB` = `rmse_TMB`, `PCA-AGHQ` = `rmse_PCA-AGHQ`) %>%
  mutate(
    Difference = `PCA-AGHQ` - TMB,
    `Percent Difference` =  (`PCA-AGHQ` - TMB) / TMB
  ) %>%
  gt::gt(groupname_col = "Type") %>%
  gt::fmt_number(
    columns = c(`TMB`, `PCA-AGHQ`, Difference),
    n_sigfig = 2
  ) %>%
 gt::fmt_percent(
    columns = `Percent Difference`,
    decimals = 1
  ) %>%
  gt::text_transform(
    locations = gt::cells_body("Parameter"),
    fn = function(x) paste0("\\texttt{", x, "}")
  ) %>%
  gt::as_latex() %>%
  as.character()
}

latex_table_point_estimates("Posterior mean estimate") %>%
  cat(file = "point-summary-mean.tex")

latex_table_point_estimates("Posterior SD estimate") %>%
  cat(file = "point-summary-sd.tex")
```

\input{point-summary-mean.tex}

### Posterior standard deviation

\input{point-summary-sd.tex}

@@

### Kolmogorov-Smirnov

@@

ks_summary %>%
  ungroup() %>%
  filter(type == "Latent field") %>%
  select(-type) %>%
  select(Parameter, TMB = `KS(TMB, tmbstan)`, `PCA-AGHQ` = `KS(aghq, tmbstan)`) %>%
  mutate(Difference = `PCA-AGHQ` - TMB) %>%
  gt::gt() %>%
  gt::summary_rows(
   columns = c(`TMB`, `PCA-AGHQ`, Difference),
   fns = list(Average = ~ mean(.x)),
   formatter = gt::fmt_number,
   decimals = 3
  ) %>%
  gt::fmt_number(
    columns = c(`TMB`, `PCA-AGHQ`, Difference),
    decimals = 3
  ) %>%
  gt::text_transform(
    locations = gt::cells_body("Parameter"),
    fn = function(x) paste0("\\texttt{", x, "}")
  ) %>%
  gt::text_transform(
    locations = gt::cells_body("Difference"),
    fn = function(x) ifelse(x < 0, paste0("\\textbf{", x, "}"), paste0(x))
  ) %>%
  gt::as_latex() %>%
  as.character() %>%
  cat(file = "ks-summary.tex")
```

### 2023-07-20 src/naomi-simple_point-estimates/point-estimates.Rmd
Add tables of point estimate estimation results to appendix #55

```{r}
df_metrics <- df_plot %>%
  group_by(method, indicator, type) %>%
  summarise(
    rmse = sqrt(mean((truth - approximate)^2)),
    mae = mean(abs(truth - approximate))
  ) %>%
  ungroup()

>>>>

```{r}
write_csv(df_plot, "point-estimates.csv")

df_metrics <- df_plot %>%
  group_by(method, indicator, type) %>%
  summarise(
    rmse = sqrt(mean((truth - approximate)^2)),
    mae = mean(abs(truth - approximate))
  ) %>%
  ungroup()
